Chromosomal duplication can be an evolutionary detour on the path to adaptation

### 2022-09-16 ms/ms.tex
added first ideas about limitations

\documentclass[12pt]{extarticle}
\usepackage{geometry}
\geometry{
a4paper,
total={170mm,257mm},
left=20mm,
top=20mm,
headheight=12pt
}
\usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx} % Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
% TeX will automatically convert eps --> pdf in pdflatex

@@

>>>>

\documentclass[12pt, draft]{extarticle}
\usepackage{geometry}
\geometry{
a4paper,
total={170mm,257mm},
left=20mm,
top=20mm,
headheight=12pt
}
\usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx} % Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
% TeX will automatically convert eps --> pdf in pdflatex

@@

% Limitations
\paragraph{Limitations and future directions}
The number of measurement of the frequency of aneuploidy in \textit{S.cervisiae} is limited to three time points (0, \~450 and \~2000).

The populations had fluctuating populations sizes due to dilution. We use the harmonic mean to determine a single number, on which all of the inference and simulations is based.

Mathematical model is very simplistic. One mutation of fixed effect, at a single locus that accounts for all the benefit. Haploid model where yest is diploid and the aneuploidy is trisomie.
